---
title: "Peer Assignment 1 - Reproducible Research"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Set the working directory where the CSV file is located.

```{r}
setwd("U:/R Directory/RepRes PA1")
```

Load the data

```{r}
library("foreign")
data<-read.csv("activity.csv", header=T)
attach(data)
summary(data)
```

## What is mean total number of steps taken per day?

Plot a histogram of the steps data, ignoring NAs

```{r}
DailySteps<-tapply(data$steps,data$date,FUN=sum,na.rm=T)
hist(DailySteps, breaks=20, col="red",xlab="Steps per Day", main="Histogram of Steps")
```

Calculate the mean and median number of steps per day

```{r echo=TRUE,results="hide"}
m1<-mean(DailySteps, na.rm=T)
med1<-median(DailySteps, na.rm=T)
```

The mean number of steps per day is `r m1`. 

The median number of steps per day is `r med1`.

## What is the average daily activity pattern?

Make a time series plot of the 5-minute intervals and the average number of steps taken, averaged across all days.

```{r echo=TRUE}
avg <- aggregate(x=data$steps,by=list(data$interval),FUN=mean, na.rm=TRUE)
attach(avg)
plot(Group.1,x,type='l',xlab='5-minute interval',ylab='Avg. steps taken')
maxint<-avg[which.max(avg$x),1]
```

The 5-minute interval, on average, with the most steps is `r maxint`.

## Imputing missing values

```{r}
NumberMissing<-sum(is.na(data$steps))
```

There are `r NumberMissing` missing values in the dataset.

## Are there differences in activity patterns between weekdays and weekends?
